My title

### 2023-03-17 outputs/paper/paper.qmd
select more variables change the plots and tables

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

model<-lm(educ~mapres10+papres10+paeduc+maeduc,data=raw_data)
summary(model)
pairs(raw_data)
# ggplot(penguins, aes(x = island, fill = species)) +
#   geom_bar(alpha = 0.8) +
#   scale_fill_manual(values = c("darkorange","purple","cyan4"),
#                     guide = "none") +
#   theme_minimal() +
#   facet_wrap(~species, ncol = 1) +
#   coord_flip()
```

@@

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(raw_data, aes(x = papres10, y = educ)) +
  geom_point(alpha=0.3)
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ruibo Sun
thanks: "https://github.com/ruibosun/how-parents-affect-childrens-education"
date: "`r Sys.time()`"
date-format: "12-03-2023"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
#bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
library(broom)
library(knitr)
library(kableExtra)
library(tidyverse)
library(dplyr)
library(here)
library(haven)
library(scales)
library(dplyr)
library(purrr)
library(forcats)
```

```{r,echo=FALSE}
cleaned_data <- read_csv(
  file = here("inputs/data/GSS2021 2.csv"))
```

@@

```{r}
#| label: fig-bills1
#| fig-cap: Bills of penguins
#| echo: false

# Fit the model
model <- lm(educ ~ mapres10 + papres10 + paeduc + maeduc, data = cleaned_data)

# Get the summary statistics and tidy them up
tidy_summary <- tidy(summary(model))

# Create a data frame for the tidy summary
summary_df <- as.data.frame(tidy_summary)

# # Rename the row names
# row_names <- c("Intercept", "Mother's Prestiges Score", "Father's Prestiges Score", "Father's Education", "Mother's Education")
# rownames(summary_df) <- row_names

# # Rename the column names
# col_names <- c("Term", "Estimate", "Std. Error", "t value", "Pr(>|t|)")
# colnames(summary_df) <- col_names
# 
# # Print the summary table with kableExtra
# library(kableExtra)
# kable(summary_df, align = c("l", "r", "r", "r", "r"), 
#       caption = "Summary of Linear Regression Model",) %>%
#   kable_styling(bootstrap_options = "striped", full_width = FALSE)

```
```{r}
#| label: fig-billssssss0
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

#level_order <- c(NA, "less than high school", "high school", "associate/junior college", "bachelor's", "graduate")

tb1 <- cleaned_data %>% 
  count(degree) %>% 
  mutate(percent=percent(x=n/sum(n))) %>% 
  rename(Degree = degree, Frequency = n, Proportion = percent)

#tb1$Degree <- factor(tb1$Degree, levels = level_order)
tb1<-tb1%>%arrange(factor(tb1$Degree,c("graduate", "bachelor's", "associate/junior college", "high school", "less than high school", NA)))

  # arrange(Degree) %>% 
  # mutate(Degree = fct_relevel(Degree, "less than high school", "high school", "associate/junior college", "bachelor's", "graduate", .missing = "NA"))

tb1%>%kable(booktabs = TRUE)
```

```{r}
#| label: fig-billssssss2
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(data = cleaned_data, aes(x = educ)) +

  geom_histogram(aes(y = ..density..), binwidth = 2, fill = "white") +
  geom_density(alpha = .2, fill = "lightblue") +

  # geom_histogram(bins = 15, fill = "lightblue", color = "white") +
  labs(title = "Histogram of Respondents' Education", x = "Education (in Years)", y = "Desensity") +
   scale_x_continuous(breaks = seq(0, 20, by = 1))+
  theme_bw()
```

```{r}
#| label: fig-billssssss3
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = mapres10)) +
  geom_histogram(aes(y = ..density.., fill = "mapres10"), alpha = 1, binwidth = 2,color = "black") +
  geom_histogram(aes(x = papres10, y = ..density.., fill = "paeduc"), alpha = 0.4, binwidth = 2,color = "black") +
  scale_fill_manual(values = c("mapres10" = "lightblue", "paeduc" = "red"), name = "Variables") +
  labs(title = "Difference between Mother's and Father's Prestige Score",
       x = "Prestige Score",
       y = "Density")+
  theme_bw()
```

```{r}
#| label: fig-billssssss4
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = maeduc)) +
  geom_histogram(aes(y = ..density.., fill = "maeduc"), alpha = 1, binwidth = 1, color = "black") +
  geom_histogram(aes(x = paeduc, y = ..density.., fill = "paeduc"), alpha = 0.4, binwidth = 1, color = "black") +
  scale_fill_manual(values = c("maeduc" = "lightblue", "paeduc" = "red"), name = "Variables") +
  labs(title = "Differene between Mother's Education and Father's Education",
       x = "Education (in Years)",
       y = "Density") +
  theme_bw()
```

@@

```{r}
#| label: fig-billssssss5
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(cleaned_data, aes(x = educ, fill = factor(born))) +
  geom_histogram(position = "dodge", binwidth = 1.5, alpha = 0.5, color = "black")+
   labs(title = "Education and Birthplace (if outside of US) for the Respondent",
       x = "Education (in Years)",
       y = "Count",
       fill = "Birthplace of the Respondent \n (if outside of US)")+
  theme_bw()
```

```{r}
#| label: fig-billssssss6
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ,fill = factor(reg16))) +
  geom_histogram(binwidth = 2, color = "black") +
  facet_wrap(~ reg16, ncol = 3)+
  labs(title = "Respondent's Living Region at Age of 16 v.s. Education",
       x = "Education (in Years)",
       y = "Count")+
  theme_bw()+
  theme(legend.position = "none")
```

```{r}
#| label: fig-billssssss7
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = maeduc, y = paeduc, color = factor(incom16))) +
  geom_point() +
  stat_smooth(method = "loess", se = FALSE) +
  labs(x = "Mother's Education (in Years)", y = "Father's Education (in Years)", color = "Family Income")+
  theme_bw()
```
